Supplementary information for ``CLM5-PPE"

### 2025-05-29 ms/supp.tex

\begin{landscape}
\begin{figure}[h]
\centering
\includegraphics[width=60pc]{../figs/supp/ilamb_lines.png}
\caption{The convergence of several scoring metrics with increasing sparsegrid resolution across a variety of CLM variables. All scores tend towards 1 as the number of sparsegrid clusters (k) approaches the 5666 gridcells for the native resolution of our 2-degree simulations. }
\label{supp:ilamb}
\end{figure}
\end{landscape}

>>>>

\begin{landscape}
\begin{figure}[h]
\centering
\includegraphics[width=60pc]{../figs/supp/ilamb_lines.png}
\caption{The convergence of several scoring metrics (based on the ILAMB2.5 benchmarking software, Collier et al. 2018) with increasing sparsegrid resolution across a variety of CLM variables. All scores tend towards 1 as the number of sparsegrid clusters (k) approaches the 5666 grid cells for the native resolution of our 2-degree simulations. }
\label{supp:ilamb}
\end{figure}
\end{landscape}
